---
title: "test2_1"
author: "sharon"
date: "2022-12-12"
output: html_document
---

> My question is "are the evicitions in 2020 for New York spatially random or do they exhibit clustering"

> A question for Spatial autocorrelation..."are the densitites of evicitions in New York similar over commnity districts for 2020" 

* we could combine a few of these questions...

> A question for spatial regression..."What are the factors that might lead to variation in evictions across New York in 2020?"

```{r}
library(tidyverse)
library(tmap)
library(geojsonio)
library(plotly)
library(rgdal)
library(broom)
library(mapview)
library(crosstalk)
library(sf)
library(sp)
library(spdep)
library(car)
library(fs)
library(janitor)
library(spatstat)

```


```{r}
#use grafftti3 and shp2

#filter something
graffiti4<- graffiti3%>%
filter(str_detect(Closed, "2019")) %>%
  #filter(str_detect(`Request Type`, "Building"))%>%
  st_transform(., crs=7131)

#clip
# spatial filter points within the san fran polygon (sf object)
#must use st_intersects?
graffiti_within <- graffiti4[shp2, ,op=st_intersects]

shp_se <- filter(shp2, geoid10=="06075016500")
graffiti_se <- graffiti4[shp_se, ,op=st_intersects]

tmap_mode("plot")
tm_shape(shp_se) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(graffiti_se) +
  tm_dots(col = "blue")


```


```{r}
#whole nyc
window <- as.owin(shp2)
plot(window)

#create a sp object
graffiti_sp <- graffiti_within %>%
  as(., 'Spatial')

#create a ppp object
graffiti_sp.ppp <- ppp(x=graffiti_sp@coords[,1],
                          y=graffiti_sp@coords[,2],
                          window=window)

#just one district
window <- as.owin(shp_se)
plot(window)

#create a sp object
graffiti_se_sp <- graffiti_se %>%
  as(., 'Spatial')

#create a ppp object
graffiti_se_sp.ppp <- ppp(x=graffiti_se_sp@coords[,1],
                          y=graffiti_se_sp@coords[,2],
                          window=window)
```


```{r}
#ripley k
#whole nyc
K1 <- graffiti_sp.ppp %>%
  Kest(., correction="border") %>%
  plot()

#just one district
K <- graffiti_se_sp.ppp %>%
  Kest(., correction="border") %>%
  plot()
```


```{r}

#first extract the points from the spatial points data frame
points_todf <- graffiti_se_sp %>%
  coordinates(.)%>%
  as.data.frame()

#now run the dbscan analysis
points_todf_DBSCAN <- points_todf %>%
  fpc::dbscan(.,eps = 50, MinPts = 30)

#based on the knee
#拐弯处
#is it useful??
# points_todf%>%
#   dbscan::kNNdistplot(., k=20)

#now quickly plot the results
plot(points_todf_DBSCAN, points_todf, main = "DBSCAN Output", frame = F)
plot(shp2$geometry, add=T)
```


```{r}
points_todf<- points_todf %>%
  mutate(dbcluster=points_todf_DBSCAN$cluster)

tosf <- points_todf%>%
  st_as_sf(., coords = c("coords.x1", "coords.x2"), 
                   crs = 7131)%>%
  filter(dbcluster>0)

ggplot(data = shp_se) +
  # add the geometry of the community areas
  geom_sf() +
  # add the geometry of the points - i have had to set the data here to add the layer
  geom_sf(data = tosf, size = 0.4, colour=tosf$dbcluster, fill=tosf$dbcluster)
```

```{r}
library(tmap)
library(sf)

#tmaptools::palette_explorer()
library(RColorBrewer)
library(tmaptools)

colours<- get_brewer_pal("Set1", n = 19)

tmap_mode("plot")
tm_shape(shp_se) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(tosf) +
  tm_dots(col = "dbcluster",  palette = colours, style = "cat")
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

